### 2025-03-26 my_paper/manuscript_main.tex
edit mistakes out

Among individuals of Asian ancestry, I find that higher bias---against Asians---is correlated with a lower self-reported Asian identity among Asian immigrants. I find that an increase of one standard deviation in bias correlates with a statistically significant 9 percentage point decrease in the self-reported Asian identity among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation immigrants, and a statistically significant 8 percentage point decrease in the self-reported Asian identity among third-generation immigrants. Additionally, a one standard deviation increase in bias is correlated with a 5 percentage points (insignificant) drop in self-reported Asian identity among second-generation Asian children with both parents born in a Asian country, a 15 percentage point decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage point decrease in self-reported Asian identity among children of White fathers-Asian mothers. Consequently, as the more economically successful Asian immigrants---educated and wealthy immigrants---may self-report Asian identity, economic research using subjective ethnic measures will underestimate White-Asian gaps in the most biased states.

@@

The objective measure of identity---unlike the self-reported measure where respondents answer affirmatively when asked if they are Asian---depends on the birthplaces of the individual, their two parents, and four grandparents. Thus, the three identifiable generations are: 1) first-generation immigrants that are born in an Asian country with both parents also being born in an Asian country, 2) second-generation immigrants are native-born citizens to at least one parent that was born in an Asian country, 3) third-generation immigrants are native-born citizens to two native-born parents and at least one grandparent that was born in an Asian country.\footnote{I restrict first-generation immigrants whose parents were born in a Spanish country to avoid including naturally born US citizens that were born abroad to US parents.} I restrict the sample to Asian, first-, second-, and third-generation immigrants who are 17 year old and younger and still live with their parents between 2004 and 2021. I present a summary of the sample statistics in the Table (\ref{tab:sumstat1}).

@@

Where $BirthPlaceMigration_{ist}^2$ is an indicator variable equal to one if person $i$ in state $s$ at the interview $t$ lives in a state that is different from his or her birth state and zero otherwise. $BirthPlaceMigration_{ilb}^2$ is an indicator variable that is equal to one if person $i$ in birthplace $l$ does not currently live in the same state he or she lived in at the year of birth $b$ and zero otherwise. The analysis, restricted to second-generation Asian immigrants with both parents born in a Asian country, uses equations (\ref{eq:migration-3}) and (\ref{eq:migration-4}).

@@

Where $Y_{ist} \equiv Bias_{ist} -  Bias_{ilb}$, $Bias_{ist}$ is $i$'s bias in state $s$ at the time of interview $t$, and  $Bias_{ilb}$ is $i$'s bias in birth state $l$ at the birth year $b$. The analysis is restricted to second-generation Asian immigrants with both parents born in a Asian country who migrated from the state they were born in $b$ to another state $s$.

>>>>

Among individuals of Asian ancestry, I find that higher bias---against Asians---is correlated with a lower self-reported Asian identity among Asian immigrants. I find that an increase of one standard deviation in bias correlates with a statistically significant 9 percentage point decrease in the self-reported Asian identity among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation immigrants, and a statistically significant 8 percentage point decrease in the self-reported Asian identity among third-generation immigrants. Additionally, a one standard deviation increase in bias is correlated with a 5 percentage points (insignificant) drop in self-reported Asian identity among second-generation Asian children with both parents born in an Asian country, a 15 percentage point decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage point decrease in self-reported Asian identity among children of White fathers-Asian mothers. Consequently, as the more economically successful Asian immigrants---educated and wealthy immigrants---may self-report Asian identity, economic research using subjective ethnic measures will underestimate White-Asian gaps in the most biased states.

@@

The objective measure of identity---unlike the self-reported measure where respondents answer affirmatively when asked if they are Asian---depends on the birthplaces of the individual, their two parents, and four grandparents. Thus, the three identifiable generations are: 1) first-generation immigrants that are born in an Asian country with both parents also being born in an Asian country, 2) second-generation immigrants are native-born citizens to at least one parent that was born in an Asian country, 3) third-generation immigrants are native-born citizens to two native-born parents and at least one grandparent that was born in an Asian country.\footnote{I restrict first-generation immigrants whose parents were born in an Asian country to avoid including naturally born US citizens that were born abroad to US parents.} I restrict the sample to Asian, first-, second-, and third-generation immigrants who are 17 year old and younger and still live with their parents between 2004 and 2021. I present a summary of the sample statistics in the Table (\ref{tab:sumstat1}).

@@

Where $BirthPlaceMigration_{ist}^2$ is an indicator variable equal to one if person $i$ in state $s$ at the interview $t$ lives in a state that is different from his or her birth state and zero otherwise. $BirthPlaceMigration_{ilb}^2$ is an indicator variable that is equal to one if person $i$ in birthplace $l$ does not currently live in the same state he or she lived in at the year of birth $b$ and zero otherwise. The analysis, restricted to second-generation Asian immigrants with both parents born in an Asian country, uses equations (\ref{eq:migration-3}) and (\ref{eq:migration-4}).

@@

Where $Y_{ist} \equiv Bias_{ist} -  Bias_{ilb}$, $Bias_{ist}$ is $i$'s bias in state $s$ at the time of interview $t$, and  $Bias_{ilb}$ is $i$'s bias in birth state $l$ at the birth year $b$. The analysis is restricted to second-generation Asian immigrants with both parents born in an Asian country who migrated from the state they were born in $b$ to another state $s$.

### 2025-03-26 submissions/01-jope/manuscript_main.tex
edit mistakes out

Among individuals of Asian ancestry, I find that higher bias---against Asians---is correlated with a lower self-reported Asian identity among Asian immigrants. I find that an increase of one standard deviation in bias correlates with a statistically significant 9 percentage point decrease in the self-reported Asian identity among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation immigrants, and a statistically significant 8 percentage point decrease in the self-reported Asian identity among third-generation immigrants. Additionally, a one standard deviation increase in bias is correlated with a 5 percentage points (insignificant) drop in self-reported Asian identity among second-generation Asian children with both parents born in a Asian country, a 15 percentage point decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage point decrease in self-reported Asian identity among children of White fathers-Asian mothers. Consequently, as the more economically successful Asian immigrants---educated and wealthy immigrants---may self-report Asian identity, economic research using subjective ethnic measures will underestimate White-Asian gaps in the most biased states.

@@

Where $interracial_{ist}^2$ is an indicator variable that is equal to one if a couple is interracial, i.e., a Asian husband-White wife or a White husband-Asian wife. $Bias_{st}$ is the average bias in state $s$ at time $t$, and $X_{ist}^2$ is a vector of partner-specific controls that would affect a marriage match that includes the wife's and husband's education, age, and years since immigrating to the United States.

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 4 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in bias is associated with 1 percentage points decrease in the chances of a Asian husband marrying a White wife. A one standard deviation increase in bias is associated a 3 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.

@@

Where $BirthPlaceMigration_{ist}^2$ is an indicator variable equal to one if person $i$ in state $s$ at the interview $t$ lives in a state that is different from his or her birth state and zero otherwise. $BirthPlaceMigration_{ilb}^2$ is an indicator variable that is equal to one if person $i$ in birthplace $l$ does not currently live in the same state he or she lived in at the year of birth $b$ and zero otherwise. The analysis, restricted to second-generation Asian immigrants with both parents born in a Asian country, uses equations (\ref{eq:migration-3}) and (\ref{eq:migration-4}).

@@

Where $Y_{ist} \equiv Bias_{ist} -  Bias_{ilb}$, $Bias_{ist}$ is $i$'s bias in state $s$ at the time of interview $t$, and  $Bias_{ilb}$ is $i$'s bias in birth state $l$ at the birth year $b$. The analysis is restricted to second-generation Asian immigrants with both parents born in a Asian country who migrated from the state they were born in $b$ to another state $s$.

>>>>

Among individuals of Asian ancestry, I find that higher bias---against Asians---is correlated with a lower self-reported Asian identity among Asian immigrants. I find that an increase of one standard deviation in bias correlates with a statistically significant 9 percentage point decrease in the self-reported Asian identity among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation immigrants, and a statistically significant 8 percentage point decrease in the self-reported Asian identity among third-generation immigrants. Additionally, a one standard deviation increase in bias is correlated with a 5 percentage points (insignificant) drop in self-reported Asian identity among second-generation Asian children with both parents born in An Asian country, a 15 percentage point decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage point decrease in self-reported Asian identity among children of White fathers-Asian mothers. Consequently, as the more economically successful Asian immigrants---educated and wealthy immigrants---may self-report Asian identity, economic research using subjective ethnic measures will underestimate White-Asian gaps in the most biased states.

@@

Where $interracial_{ist}^2$ is an indicator variable that is equal to one if a couple is interracial, i.e., An Asian husband-White wife or a White husband-Asian wife. $Bias_{st}$ is the average bias in state $s$ at time $t$, and $X_{ist}^2$ is a vector of partner-specific controls that would affect a marriage match that includes the wife's and husband's education, age, and years since immigrating to the United States.

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 4 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in bias is associated with 1 percentage points decrease in the chances of An Asian husband marrying a White wife. A one standard deviation increase in bias is associated a 3 percentage points increase in the chances of An Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.

@@

Where $BirthPlaceMigration_{ist}^2$ is an indicator variable equal to one if person $i$ in state $s$ at the interview $t$ lives in a state that is different from his or her birth state and zero otherwise. $BirthPlaceMigration_{ilb}^2$ is an indicator variable that is equal to one if person $i$ in birthplace $l$ does not currently live in the same state he or she lived in at the year of birth $b$ and zero otherwise. The analysis, restricted to second-generation Asian immigrants with both parents born in An Asian country, uses equations (\ref{eq:migration-3}) and (\ref{eq:migration-4}).

@@

Where $Y_{ist} \equiv Bias_{ist} -  Bias_{ilb}$, $Bias_{ist}$ is $i$'s bias in state $s$ at the time of interview $t$, and  $Bias_{ilb}$ is $i$'s bias in birth state $l$ at the birth year $b$. The analysis is restricted to second-generation Asian immigrants with both parents born in An Asian country who migrated from the state they were born in $b$ to another state $s$.
